### 2021-09-14 paper/localpsf.tex
paper cleanup

For each $i=1,\dots,r$, optimization problem \eqref{eq:wi_optimization_problem} is an example of the following generic optimization problem:
\begin{equation}
	\label{eq:wi_optimization_problem_generic}
	\begin{aligned}
		\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
		\text{such that} &\quad v(x_j) = \interpolatedvalues_j, \quad j=1,\dots,r,
	\end{aligned}
\end{equation}
where $\interpolatedvalues_j \in \mathbb{R}$, $j=1,\dots,r$ are now arbitrary function values that $v$ must take at the points $x_j$. We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \beta + \sum_{i=1}^r c_i \secondgreens_i(x),
	\end{equation}
	where the constants $c_i \in \mathbb{R}$, $i=1,\dots,r$, and $\beta \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			S & \mathbf{1} \\ \mathbf{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\mathbf{c} \\ \beta
		\end{bmatrix}
		=
		\begin{bmatrix}
			\mathbf{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\mathbf{c} \in \mathbb{R}^r$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^r$ is the column vector of all ones, $\mathbf{\interpolatedvalues} \in \mathbb{R}^r$ is the vector with $i$th component $\interpolatedvalues_i$, and $S \in \mathbb{R}^{r \times r}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		S_{ij} := \int_\Omega \firstgreens_i(x) \firstgreens_j(x) dx.
	\end{equation}
\end{enumerate}
In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, so long as there is no repetition in the points $x_i$. Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $r+1$-dimensional subspace spanned by the functions $\firstgreens_i$, $i=1,\dots,r$, and the constant function $C(x)=1$, rather than solving the optimization problem on the infinite dimensional space $H^2_N(\Omega)$. In Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this process solves optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

Let $f_1, f_2, \dots, f_N$ be a set of finite element basis functions used to discretize the problem on a mesh with mesh size parameter $h$, and let $V_h := \Span\left(f_1, f_2, \dots, f_N\right)$ be the corresponding finite element space. Further, let $p_i \in \mathbb{R}^d$, $i=1,\dots, N$ be the Lagrange nodes associated with the functions $f_i$. That is, the points such that $f_i(p_j)$ equals one if $i=j$, and zero otherwise.

In Section \ref{sec:intro} we noted that the original integral kernel, $\Aker$, is inaccessible, while in Equation \eqref{eq:kernel_entries}  we saw that the integral kernel for our product-convolution approximation, $\AkerPc \approx \Aker$, is accessible, and may be cheaply evaluated at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$ via the following formula:
\begin{equation}
	\label{eq:eval_y_x}
	\AkerPc(y,x) = \sum_{i=1}^r w_i(x) \convkernel_{x_i}(y-x).
\end{equation}
We now define a further approximation, $\AkerPcMesh \approx \AkerPc$, as follows:
\begin{equation}
	\label{eq:defn_of_Akerpcmesh}
	\AkerPcMesh(y,x) := \sum_{i=1}^N \sum_{j=1}^N \AkerPc(p_i,p_j) f_i(y) f_j(x).
\end{equation}
The kernel $\AkerPcMesh$ is the interpolation of $\AkerPc$ onto $V_h \otimes V_h$. Error in the overall kernel approximation, $\AkerPcMesh \approx \Aker$, arises both because of error in the product-convolution approximation, and because of finite element discretization error incurred from interpolation onto $V_h \otimes V_h$.

Replacing $\Aker$ with $\AkerPcMesh$ within the definition of $\Aop$ in \eqref{eq:kernel_representation} yields the following operator approximation, $\AopPcMesh$:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\AopPcMesh u)(v) := \int_\Omega \int_\Omega v(y) \AkerPcMesh(y,x) u(x) dx dy.
\end{equation}
While $\AopPcMesh$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\AopPcMesh$ to functions in the finite element space. That is, $\AopPcMesh : V_h \rightarrow V_h'$. Let $u_h \in V_h$ and $v_h \in V_h$, and let $\mathbf{u}$ and $\mathbf{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $f_1, \dots, f_N$. I.e., 
\begin{equation}
	\label{eq:fem_coeff_basis}
	u_h(x) = \sum_{i=1}^N \mathbf{u}_i f_i(x),
\end{equation}
and similar for $v_h$. Further, let $\mathbf{M} \in \mathbb{R}^{N \times N}$ be the finite element mass matrix, and let $\AkerPcMat \in \mathbb{R}^{N \times N}$ be following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\left(\AkerPcMat\right)_{ij} := \AkerPcMesh(p_i, p_j).
\end{equation}
Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
\begin{equation*}
	\left(\AopPcMesh u_h \right)(v_h) = \mathbf{v}^T \mathbf{M} \AkerPcMat \mathbf{M} \mathbf{u}.
\end{equation*}
The finite element matrix representation of $\AopPcMesh$, which we denote by $\AmatPc$, is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\AmatPc := \mathbf{M} \AkerPcMat \mathbf{M}.
\end{equation}

@@

Let $f_i$, $i=1,\dots,N$ be a set of finite element basis functions, let $h$ denote the mesh size parameter for the finite element mesh, and let
\begin{equation*}
	V_h = \Span\left(f_1, f_2, \dots, f_N\right)
\end{equation*}
be the corresponding  finite element space with the $L^2$ inner product. Functions $u\in L^2(\Omega)$ are approximated by functions $u_h \in V_h$. In turn, functions $u_h\in V_h$ are represented in computations by length $N$ arrays $\mathbf{u}$, such that the array entries of $\mathbf{u}$ are the coordinates of $u_h$ in the finite element basis. That is,
\begin{equation}
	\label{eq:finite_bijection}
	u_h(x) = \sum_{i=1}^N \mathbf{u}_i f_i(x).
\end{equation}

We write $\mathbf{M} \in \mathbb{R}^{N \times N}$ to denote the finite element \emph{mass matrix}, which has entries
\begin{equation*}
	\mathbf{M}_{ij} = \left(f_i, f_j\right)_{L^2(\Omega)} = \int_{\Omega} f_i(x) f_j(x) dx,
\end{equation*}
and we write $\mathbb{R}^N_\mathbf{M}$ to denote the space $\mathbb{R}^N$ with the matrix-weighted inner product
\begin{equation*}
	\left(\mathbf{u},\mathbf{v}\right)_\mathbf{M} := \mathbf{v}^T\mathbf{M} \mathbf{u}.
\end{equation*}
Direct calculation shows that $V_h$ is isometrically isomorphic $\mathbb{R}^N_\mathbf{M}$. That is, equation \eqref{eq:finite_bijection} establishes a bijection between functions $u_h \in V_h$ and coefficient vectors $\mathbf{u} \in \mathbb{R}^N_\mathbf{M}$, and this bijection preserves the inner product in the sense that $\left(u_h, v_h\right)_{L^2(\Omega)} = \left(\mathbf{u},\mathbf{v}\right)_\mathbf{M}$. Likewise, the dual space, $V_h'$, is isometrically isomorphic to $\mathbb{R}^N_{\mathbf{M}^{-1}}$.

@@

\begin{description}
	\item[Coefficients of a functional:] The coefficient dual vector, $\boldsymbol{\sigma} \in \mathbb{R}^N_{\mathbf{M}^{-1}}$, corresponding to a linear functional $\sigma_h \in V_h'$ has components given by
	\begin{equation*}
		\boldsymbol{\sigma}_i = \sigma_h(f_i), \quad i=1,\dots,N.
	\end{equation*}
	\item[Action of a functional:] The action of a linear functional $\sigma_h \in V_h'$ on a function $u_h \in V_h$ may be computed as follows:
	\begin{equation*}
		\sigma_h(v_h) = \boldsymbol{\sigma}^T \mathbf{u}.
	\end{equation*}
	\item[Riesz representation:] Let $\sigma_h \in V_h'$. The Riesz representation of $\sigma_h$ is the unique  function $\sigma_h^* \in V_h$ satisfying 
	\begin{equation*} 
		\left(\sigma_h^*, v_h\right)_{L^2(\Omega)} = \sigma_h(v_h) \quad\forall v_h \in V_h.
	\end{equation*}
	The coefficient dual vector $\boldsymbol{\sigma}^*$ corresponding to $\sigma_h$ is given by
	\begin{equation*} 
		\boldsymbol{\sigma}^* = \mathbf{M}^{-1} \boldsymbol{\sigma}.
	\end{equation*}
	\item[Finite element $L^2$ projection:] Let $g \in L^2(\Omega)$. The orthogonal projection of $g$ onto $V_h$ with respect to the $L^2$ inner product is the unique function $g^\pi_h \in V_h$ satisfying
	\begin{equation*}
		\left(g^\pi_h, v_h\right)_{L^2(\Omega)} = \left(g, v_h\right)_{L^2(\Omega)} \quad\forall v_h \in V_h.
	\end{equation*}
	 Let $\left(\mathbf{g}^\pi\right)^* \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ be the vector with components
	\begin{equation*}
		\left(\mathbf{g}^\pi\right)^*_i = \int_\Omega g(x) f_i(x) dx, \quad i=1,\dots,N.
	\end{equation*}
	The coefficient vector $\mathbf{g}^\pi \in \mathbb{R}^N_{\mathbf{M}}$ corresponding to $g^\pi_h$ is given by
	\begin{equation*}
		\mathbf{g}^\pi = \mathbf{M}^{-1}\left(\mathbf{g}^\pi\right)^*.
	\end{equation*}
	\item[Finite element interpolation:] Let $p_i \in \mathbb{R}^d$, $i=1,\dots,N$, be the Lagrange nodes associated with the finite element basis functions $f_i$. The finite element interpolant of a function $g \in C\left(\overline{\Omega}\right)$ is the function $g^I \in V_h$ given by
	\begin{equation*}
		g_h^I(x) = \sum_{i=1}^N g(p_i) f_i(x).
	\end{equation*}
	The coefficient vector, $\mathbf{g}$, for $g_h^I$ has components 
	\begin{equation*}
	\mathbf{g}_i^I = g(p_i), \quad i=1.,\dots,N.
	\end{equation*}
	\item[Projection vs. interpolation:]
	Typically, $g^\pi$ is a more accurate approximation of $g$ than $g^I$, but $g^I$ is cheaper to compute than $g^\pi$ because computing $g^\pi$ requires solving a linear system, while computing $g^I$ does not. If the finite element basis satisfies the following Kronecker property,
	\begin{equation*}
		f_i(p_j) = \begin{cases}1 & i=j \\
		0 & \text{otherwise},\end{cases}
	\end{equation*}
	then $g^I(p_i) = g(p_i)$ for $i=1,\dots,N$ (i.e., the interpolant equals the original function at the Lagrange nodes). Interpolation is typically sufficiently accurate for practical purposes if the Kronecker property is satisfied. Projection should be used if the Kronecker property is not satisfied.
	\item[Matrix representation of an operator:] Let $\mathcal{B}_h : V_h \rightarrow V_h'$ be a linear operator, and let $\mathbf{B} \in \mathbf{R}^{N \times N}$ be the matrix with entries
	\begin{equation*}
		\mathbf{B}_{ij} = \left(\mathcal{B}_h f_j\right)(f_i).
	\end{equation*}
	The matrix $\mathbf{B}$ maps $\mathbb{R}^N_\mathbf{M} \rightarrow \mathbb{R}^N_{\mathbf{M}^{-1}}$ by matrix multiplication, and
	\begin{equation*}
		\sigma_h = \mathcal{B}_h u_h \quad \Leftrightarrow \quad \boldsymbol{\sigma} = \mathbf{B} \mathbf{u}.
	\end{equation*}
	\item[Transpose:] The matrix $\mathbf{B}^T$ maps $\mathbb{R}^N_\mathbf{M} \rightarrow \mathbb{R}^N_{\mathbf{M}^{-1}}$ via matrix multiplication, and
	\begin{equation*}
		\sigma_h = \mathcal{B}_h^T u_h \quad \Leftrightarrow \quad \boldsymbol{\sigma} = \mathbf{B}^T \mathbf{u}.
	\end{equation*}

	\item[Distributions:] Let $\mu:C\left(\overline{\Omega}\right)\rightarrow \mathbb{R}$ be a distribution. If $\mu(f_i)$ is well-defined for $i=1,\dots,N$, then the restriction of $\mu$ to domain $V_h$ is a linear functional $\mu_h\in V_h'$. The functional $\mu_h$ has a coefficient dual vector $\boldsymbol{\mu} \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ with entries 
	\begin{equation*}
		\boldsymbol{\mu}_i=\mu(f_i), \quad i=1,\dots,N.
	\end{equation*} 
	For example, let $\delta_p$ be the Dirac distribution centered at a point $p\in\Omega$. If the finite element basis functions, $f_i$, are continuous at $p$, then restricting the domain of $\delta_p$ to the space $V_h$ yields a linear functional in $V_h'$. The corresponding coefficient dual vector, $\boldsymbol{\delta}_p$, has entries 
	\begin{equation*}
		\left(\boldsymbol{\delta}_p\right)_i = f_i(p), \quad i=1,\dots,N.
	\end{equation*}

@@

\subsection{Discretized sampling of impulse responses}
In computations, the Dirac comb coefficient dual vector for $\dcomb_h^b$ is the vector $\boldsymbol{\dcomb}^b \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ which has entries
\begin{equation*}
	\boldsymbol{\dcomb}^b_i = \sum_{x_j \in S_b} f_i(x_j), \quad i=1,\dots,N.
\end{equation*}
The Dirac comb impulse response coefficient vector for $\combresponse^h_b$ is the vector $\boldsymbol{\combresponse}_b \in \mathbb{R}^N_\mathbf{M}$ given by
\begin{equation*}
	\boldsymbol{\combresponse}_b = \mathbf{M}^{-1} \mathbf{A}^T \mathbf{M}^{-1}\boldsymbol{\dcomb}^b.
\end{equation*}

>>>>

For each $i=1,\dots,r$, optimization problem \eqref{eq:wi_optimization_problem} is an example of the following generic optimization problem:
\begin{equation}
	\label{eq:wi_optimization_problem_generic}
	\begin{aligned}
		\min_{v \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta v}_{L^2(\Omega)}^2 \\
		\text{such that} &\quad v(x_j) = \interpolatedvalues_j, \quad j=1,\dots,r,
	\end{aligned}
\end{equation}
where $\interpolatedvalues_j \in \mathbb{R}$, $j=1,\dots,r$ are now arbitrary function values that $v$ must take at the points $x_j$. We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \beta + \sum_{i=1}^r c_i \secondgreens_i(x),
	\end{equation}
	where the constants $c_i \in \mathbb{R}$, $i=1,\dots,r$, and $\beta \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			S & \mathbf{1} \\ \mathbf{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\mathbf{c} \\ \beta
		\end{bmatrix}
		=
		\begin{bmatrix}
			\mathbf{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\mathbf{c} \in \mathbb{R}^r$ is the vector with $i$th component $c_i$, $\mathbf{1} \in \mathbf{R}^r$ is the column vector of all ones, $\mathbf{\interpolatedvalues} \in \mathbb{R}^r$ is the vector with $i$th component $\interpolatedvalues_i$, and $S \in \mathbb{R}^{r \times r}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		S_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, so long as there is no repetition in the points $x_i$. Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $r+1$-dimensional subspace spanned by the functions $\firstgreens_i$, $i=1,\dots,r$, and the constant function $C(x)=1$, rather than solving the optimization problem on the infinite dimensional space $H^2_N(\Omega)$. In Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this process solves optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

Let $\febasis_1, \febasis_2, \dots, febasis_N$ be a set of finite element basis functions used to discretize the problem on a mesh with mesh size parameter $h$, and let $V_h := \Span\left(\febasis_1, \febasis_2, \dots, \febasis_N\right)$ be the corresponding finite element space. Further, let $p_i \in \mathbb{R}^d$, $i=1,\dots, N$ be the Lagrange nodes associated with the functions $\febasis_i$. That is, the points such that $\febasis_i(p_j)$ equals one if $i=j$, and zero otherwise.

In Section \ref{sec:intro} we noted that the original integral kernel, $\Aker$, is inaccessible, while in Equation \eqref{eq:kernel_entries}  we saw that the integral kernel for our product-convolution approximation, $\AkerPc \approx \Aker$, is accessible, and may be cheaply evaluated at arbitrary pairs of points $(y,x) \in \Omega \times \Omega$ via the following formula:
\begin{equation}
	\label{eq:eval_y_x}
	\AkerPc(y,x) = \sum_{i=1}^r w_i(x) \convkernel_{x_i}(y-x).
\end{equation}
We now define a further approximation, $\AkerPcMesh \approx \AkerPc$, as follows:
\begin{equation}
	\label{eq:defn_of_Akerpcmesh}
	\AkerPcMesh(y,x) := \sum_{i=1}^N \sum_{j=1}^N \AkerPc(p_i,p_j) \febasis_i(y) \febasis_j(x).
\end{equation}
The kernel $\AkerPcMesh$ is the interpolation of $\AkerPc$ onto $V_h \otimes V_h$. Error in the overall kernel approximation, $\AkerPcMesh \approx \Aker$, arises both because of error in the product-convolution approximation, and because of finite element discretization error incurred from interpolation onto $V_h \otimes V_h$.

Replacing $\Aker$ with $\AkerPcMesh$ within the definition of $\Aop$ in \eqref{eq:kernel_representation} yields the following operator approximation, $\AopPcMesh$:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\AopPcMesh u)(v) := \int_\Omega \int_\Omega v(y) \AkerPcMesh(y,x) u(x) dx dy.
\end{equation}
While $\AopPcMesh$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\AopPcMesh$ to functions in the finite element space. That is, $\AopPcMesh : V_h \rightarrow V_h'$. Let $u_h \in V_h$ and $v_h \in V_h$, and let $\mathbf{u}$ and $\mathbf{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $\febasis_1, \dots, \febasis_N$. I.e., 
\begin{equation}
	\label{eq:fem_coeff_basis}
	u_h(x) = \sum_{i=1}^N \mathbf{u}_i \febasis_i(x),
\end{equation}
and similar for $v_h$. Further, let $\mathbf{M} \in \mathbb{R}^{N \times N}$ be the finite element mass matrix, and let $\AkerPcMat \in \mathbb{R}^{N \times N}$ be following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\left(\AkerPcMat\right)_{ij} := \AkerPcMesh(p_i, p_j).
\end{equation}
Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
\begin{equation*}
	\left(\AopPcMesh u_h \right)(v_h) = \mathbf{v}^T \mathbf{M} \AkerPcMat \mathbf{M} \mathbf{u}.
\end{equation*}
The finite element matrix representation of $\AopPcMesh$, which we denote by $\AmatPc$, is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\AmatPc := \mathbf{M} \AkerPcMat \mathbf{M}.
\end{equation}

@@

Let $\febasis_i$, $i=1,\dots,N$ be a set of finite element basis functions, let $h$ denote the mesh size parameter for the finite element mesh, and let
\begin{equation*}
	V_h = \Span\left(\febasis_1, \febasis_2, \dots, \febasis_N\right)
\end{equation*}
be the corresponding  finite element space with the $L^2$ inner product. Functions $u\in L^2(\Omega)$ are approximated by functions $u_h \in V_h$. In turn, functions $u_h\in V_h$ are represented in computations by length $N$ arrays $\mathbf{u}$, such that the array entries of $\mathbf{u}$ are the coordinates of $u_h$ in the finite element basis. That is,
\begin{equation}
	\label{eq:finite_bijection}
	u_h(x) = \sum_{i=1}^N \mathbf{u}_i \febasis_i(x).
\end{equation}

We write $\mathbf{M} \in \mathbb{R}^{N \times N}$ to denote the finite element \emph{mass matrix}, which has entries
\begin{equation*}
	\mathbf{M}_{ij} = \left(\febasis_i, \febasis_j\right)_{L^2(\Omega)} = \int_{\Omega} \febasis_i(x) \febasis_j(x) dx,
\end{equation*}
and we write $\mathbb{R}^N_\mathbf{M}$ to denote the space $\mathbb{R}^N$ with the matrix-weighted inner product
\begin{equation*}
	\left(\mathbf{u},\mathbf{v}\right)_\mathbf{M} := \mathbf{v}^T\mathbf{M} \mathbf{u}.
\end{equation*}
Direct calculation shows that $V_h$ is isometrically isomorphic $\mathbb{R}^N_\mathbf{M}$. That is, equation \eqref{eq:finite_bijection} establishes a bijection between functions $u_h \in V_h$ and coefficient vectors $\mathbf{u} \in \mathbb{R}^N_\mathbf{M}$, and this bijection preserves the inner product in the sense that $\left(u_h, v_h\right)_{L^2(\Omega)} = \left(\mathbf{u},\mathbf{v}\right)_\mathbf{M}$. Likewise, the dual space, $V_h'$, is isometrically isomorphic to $\mathbb{R}^N_{\mathbf{M}^{-1}}$.

@@

\begin{description}
	\item[Coefficients of a functional:] The coefficient dual vector, $\boldsymbol{\sigma} \in \mathbb{R}^N_{\mathbf{M}^{-1}}$, corresponding to a linear functional $\sigma_h \in V_h'$ has components given by
	\begin{equation*}
		\boldsymbol{\sigma}_i = \sigma_h(\febasis_i), \quad i=1,\dots,N.
	\end{equation*}
	\item[Action of a functional:] The action of a linear functional $\sigma_h \in V_h'$ on a function $u_h \in V_h$ may be computed as follows:
	\begin{equation*}
		\sigma_h(v_h) = \boldsymbol{\sigma}^T \mathbf{u}.
	\end{equation*}
	\item[Riesz representation:] Let $\sigma_h \in V_h'$. The Riesz representation of $\sigma_h$ is the unique  function $\sigma_h^* \in V_h$ satisfying 
	\begin{equation*} 
		\left(\sigma_h^*, v_h\right)_{L^2(\Omega)} = \sigma_h(v_h) \quad\forall v_h \in V_h.
	\end{equation*}
	The coefficient dual vector $\boldsymbol{\sigma}^*$ corresponding to $\sigma_h$ is given by
	\begin{equation*} 
		\boldsymbol{\sigma}^* = \mathbf{M}^{-1} \boldsymbol{\sigma}.
	\end{equation*}
	\item[Finite element $L^2$ projection:] Let $g \in L^2(\Omega)$. The orthogonal projection of $g$ onto $V_h$ with respect to the $L^2$ inner product is the unique function $g^\pi_h \in V_h$ satisfying
	\begin{equation*}
		\left(g^\pi_h, v_h\right)_{L^2(\Omega)} = \left(g, v_h\right)_{L^2(\Omega)} \quad\forall v_h \in V_h.
	\end{equation*}
	 Let $\left(\mathbf{g}^\pi\right)^* \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ be the vector with components
	\begin{equation*}
		\left(\mathbf{g}^\pi\right)^*_i = \int_\Omega g(x) \febasis_i(x) dx, \quad i=1,\dots,N.
	\end{equation*}
	The coefficient vector $\mathbf{g}^\pi \in \mathbb{R}^N_{\mathbf{M}}$ corresponding to $g^\pi_h$ is given by
	\begin{equation*}
		\mathbf{g}^\pi = \mathbf{M}^{-1}\left(\mathbf{g}^\pi\right)^*.
	\end{equation*}
	\item[Finite element interpolation:] Let $p_i \in \mathbb{R}^d$, $i=1,\dots,N$, be the Lagrange nodes associated with the finite element basis functions $\febasis_i$. The finite element interpolant of a function $g \in C\left(\overline{\Omega}\right)$ is the function $g^I \in V_h$ given by
	\begin{equation*}
		g_h^I(x) = \sum_{i=1}^N g(p_i) \febasis_i(x).
	\end{equation*}
	The coefficient vector, $\mathbf{g}$, for $g_h^I$ has components 
	\begin{equation*}
	\mathbf{g}_i^I = g(p_i), \quad i=1.,\dots,N.
	\end{equation*}
	\item[Projection vs. interpolation:]
	Typically, $g^\pi$ is a more accurate approximation of $g$ than $g^I$, but $g^I$ is cheaper to compute than $g^\pi$ because computing $g^\pi$ requires solving a linear system, while computing $g^I$ does not. If the finite element basis satisfies the following Kronecker property,
	\begin{equation*}
		\febasis_i(p_j) = \begin{cases}1 & i=j \\
		0 & \text{otherwise},\end{cases}
	\end{equation*}
	then $g^I(p_i) = g(p_i)$ for $i=1,\dots,N$ (i.e., the interpolant equals the original function at the Lagrange nodes). Interpolation is typically sufficiently accurate for practical purposes if the Kronecker property is satisfied. Projection should be used if the Kronecker property is not satisfied.
	\item[Matrix representation of an operator:] Let $\mathcal{B}_h : V_h \rightarrow V_h'$ be a linear operator, and let $\mathbf{B} \in \mathbf{R}^{N \times N}$ be the matrix with entries
	\begin{equation*}
		\mathbf{B}_{ij} = \left(\mathcal{B}_h \febasis_j\right)(\febasis_i).
	\end{equation*}
	The matrix $\mathbf{B}$ maps $\mathbb{R}^N_\mathbf{M} \rightarrow \mathbb{R}^N_{\mathbf{M}^{-1}}$ by matrix multiplication, and
	\begin{equation*}
		\sigma_h = \mathcal{B}_h u_h \quad \Leftrightarrow \quad \boldsymbol{\sigma} = \mathbf{B} \mathbf{u}.
	\end{equation*}
	\item[Transpose:] The matrix $\mathbf{B}^T$ maps $\mathbb{R}^N_\mathbf{M} \rightarrow \mathbb{R}^N_{\mathbf{M}^{-1}}$ via matrix multiplication, and
	\begin{equation*}
		\sigma_h = \mathcal{B}_h^T u_h \quad \Leftrightarrow \quad \boldsymbol{\sigma} = \mathbf{B}^T \mathbf{u}.
	\end{equation*}

	\item[Distributions:] Let $\mu:C\left(\overline{\Omega}\right)\rightarrow \mathbb{R}$ be a distribution. If $\mu(\febasis_i)$ is well-defined for $i=1,\dots,N$, then the restriction of $\mu$ to domain $V_h$ is a linear functional $\mu_h\in V_h'$. The functional $\mu_h$ has a coefficient dual vector $\boldsymbol{\mu} \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ with entries 
	\begin{equation*}
		\boldsymbol{\mu}_i=\mu(\febasis_i), \quad i=1,\dots,N.
	\end{equation*} 
	For example, let $\delta_p$ be the Dirac distribution centered at a point $p\in\Omega$. If the finite element basis functions, $\febasis_i$, are continuous at $p$, then restricting the domain of $\delta_p$ to the space $V_h$ yields a linear functional in $V_h'$. The corresponding coefficient dual vector, $\boldsymbol{\delta}_p$, has entries 
	\begin{equation*}
		\left(\boldsymbol{\delta}_p\right)_i = \febasis_i(p), \quad i=1,\dots,N.
	\end{equation*}

@@

\subsection{Discretized sampling of impulse responses}
In computations, the Dirac comb coefficient dual vector for $\dcomb_h^b$ is the vector $\boldsymbol{\dcomb}^b \in \mathbb{R}^N_{\mathbf{M}^{-1}}$ which has entries
\begin{equation*}
	\boldsymbol{\dcomb}^b_i = \sum_{x_j \in S_b} \febasis_i(x_j), \quad i=1,\dots,N.
\end{equation*}
The Dirac comb impulse response coefficient vector for $\combresponse^h_b$ is the vector $\boldsymbol{\combresponse}_b \in \mathbb{R}^N_\mathbf{M}$ given by
\begin{equation*}
	\boldsymbol{\combresponse}_b = \mathbf{M}^{-1} \mathbf{A}^T \mathbf{M}^{-1}\boldsymbol{\dcomb}^b.
\end{equation*}
